### 2024-03-31 docs/SOSP 2024/caching.tex
Add sections for schedule space exploration and introduction

\section{Exploring the Schedule Space}
\TODO{Motivate the need for schedule space exploration (maybe some initial numbers on how different the perf is with different schedules?
The histograms maybe?). Then motivate the need for a search space exploration tool (present some numbers on how long schedule exploration takes).}

>>>>

\section{Exploring the Schedule Space}
\label{sec:exploring}

\begin{itemize}
  \item The scheduling language described in Section \ref{sec:schedule} allows for numerous possible schedules for a given model. 
  Finding a schedule with good performance is a non-trivial task.
  \item We identify a reasonable template schedule for GPUs which encompasses all strategies published in prior work.
  \item Describe the template schedule.
  \item Even within the variants of this template schedule, there is a significant amount of variation in performance. Show the histogram. 
  \item Extensively exploring all possible parameter values for the template schedule is infeasible due to the large number of parameters.
  Cite some numbers on how long it takes to explore the schedule space.
  \item List the observations we make and the heuristic we design based on these.
\end{itemize}

The set of schedules that can be constructed using the scheduling language described in 
Section \ref{sec:schedule} is vast. Searching this schedule space to find a schedule that
provides good performance is a non-trivial task. To simplify this process, we identify a
reasonable template schedule for GPUs that encompasses all strategies published in prior work.
The template schedule exposes many parameters that can be tuned to find a 
high-performance schedule.
\begin{itemize}
  \item \textbf{Number of rows per thread block (Integer):} The number of rows that are processed by each thread block.
  \item \textbf{Number of rows per thread (Integer):} The number of rows processed by each thread.
  \item \textbf{Number of tree threads (Integer):} The number of threads across which the trees are distributed.
  \item \textbf{Cache rows (Boolean):} Whether the input rows are cached in shared memory.
  \item \textbf{Cache trees (Boolean):} Whether the trees are cached in shared memory.
  \item \textbf{Unroll walks (Boolean):} Whether the tree walks are unrolled.
  \item \textbf{Tree walk interleave factor:} The number of tree walks that are interleaved.
  \item \textbf{Shared memory reduction:} Whether the reduction across tree threads is done in shared memory.
\end{itemize}

While the template schedule simplifies optimization of generated inference code, it is 
important to note that the \Treebeard{} compiler itself does not place any 
restrictions on the schedule. The user is free to specify any schedule they wish.
The auto-scheduler that implements the template schedule is implemented as a 
module outside the core \Treebeard{} compiler. Users are also free to implement 
other auto-schedulers that generate schedules different from the template schedule.
